%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX program = xelatex
%!TeX TS-program = XeLaTeX
%!TEX encoding = UTF-8 Unicode
\documentclass[12pt, a4paper]{article}

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{textwidth=14.8cm, textheight=24.1cm, marginparsep=12pt, marginparwidth=1.5cm}
\parindent 0.0cm
\parskip 0.1cm
\linespread{1.1}
\usepackage[hyphens]{url}
\usepackage{multicol}
\setlength{\columnsep}{-1.0cm}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Scale = 1.0, Ligatures={Common}, BoldFont={Libertinus Serif Bold}, ItalicFont={Libertinus Serif Italic}]{Libertinus Serif}
% Year as margin note on left
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\reversemarginpar
% Footnotes as symbols
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

% Date formatting
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{-}

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\upshape\Large}
\subsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\subsubsectionfont{\rmfamily\mdseries\upshape\normalsize} 
% Space around headers
\usepackage{titlesec}
\titlespacing{\section}{0pt}{6pt}{4pt}
\titlespacing{\subsection}{0pt}{4pt}{2pt}

% Icons
\usepackage{fontawesome5}
\usepackage{academicons}

% List format
\usepackage{enumitem}
\setlist[itemize]{label={},itemindent=0em,leftmargin=0em,itemsep=-0.2em}

% PDF SETUP
\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={Matti Vuorre - CV},pdfauthor={Matti Vuorre}]{hyperref} 
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 
\urlstyle{same}

% Content
\begin{document}
\noindent{\LARGE Matti Vuorre}\\[4pt]
{\Large >> Curriculum vitae}
\vspace{24pt}

\setlength\multicolsep{0pt}
\begin{multicols}{2}
Department of Social Psychology\\
Tilburg University\\
Prof. Cobbenhagenlaan 225\\
5037 DB Tilburg\\
The Netherlands\\
\faIcon[regular]{envelope} \href{mailto:mjvuorre@uvt.nl}{mjvuorre@uvt.nl}\\
\vfill\null
\columnbreak
\faIcon[regular]{globe} \href{https://vuorre.com}{vuorre.com}\\
\aiOrcid \ \href{https://orcid.org/0000-0001-5052-066X}{0000-0001-5052-066X}\\
\aiPsyArXiv \ \href{https://osf.io/preprints/psyarxiv/discover?activeFilters=[{"propertyVisibleLabel":"Creator","propertyPathKey":"creator","label":"Matti%20Vuorre","value":"https://osf.io/tdyix"}]&sort=-dateCreated}{preprints} \\
\aiZenodoSquare \ \href{https://zenodo.org/search?q=metadata.creators.person_or_org.name%3A%22Matti%20Vuorre%22&l=list&p=1&s=10&sort=publication-desc}{Zenodo} \\
\faGithub \ \href{https://github.com/mvuorre}{GitHub}\\
\aiCV \ \today \ [\href{https://github.com/mvuorre/CV/raw/main/vuorre-matti.pdf}{latest}]
\end{multicols}

I am a psychological scientist at the Tilburg School for Social and Behavioral Sciences at Tilburg University, where I study how digital environments relate to cognition and well-being using experimental, data science, and statistical methods. 

\section*{Academic Positions}
\begin{itemize}
  \item \years{2023 - now} \emph{Assistant Professor}, Department of Social Psychology, Tilburg University
  \item \years{2020 - 2022} \emph{Postdoctoral Researcher}, Oxford Internet Institute, University of Oxford
  \item \years{2018 - 2020} \emph{Postdoctoral Research Scientist}, Department of Psychology, Columbia University
\end{itemize}

\section*{Education}
\begin{itemize}
  \item \years{2018}\textsc{PhD}, Columbia University, USA
  \item \years{2015}\textsc{M.A}, Columbia University, USA
  \item \years{2013}\textsc{BSc (Hons)}, Victoria University of Wellington, New Zealand
\end{itemize}

\section*{Research Funding}
\begin{itemize}
  \item \years{2024}Understanding the associations between online video game play and well-being in a representative Dutch sample. Tilburg University. (\emph{Co-PI with M. Klincewicz. €8,577.})
  \item How does digitalization associate with brain aging? Tilburg University. (\emph{Co-PI with S. M. Kia. €12,000.})
  \item \years{2023}Does the nose know? Validating immersive multisensory VR food environments to study eating behaviour. Tilburg University. (\emph{Co-I with PI R. de Vries. €16,344.})
  \item \years{2022}Understanding video game play and mental health. Economic and Social Research Council. (\emph{Co-I with Co-I K. Magnusson and PI A. Przybylski. £935,050.})
  \item \years{2021}The association between video game play and cognition. University of Oxford. (\emph{PI. £10,000})
\end{itemize}

\section*{Honors \& Awards}
\begin{itemize}
  \item \years{2016}Leo Rubinstein Endowed Fellowship (Columbia University)
  \item Graduate Student Travel Award (Psychonomic Society)
  \item \years{2015}Leo Rubinstein Endowed Fellowship (Columbia University)
  \item Edward E. Smith Memorial Award in Cognitive Neuroscience (Columbia University)
  \item Best Student Poster Award (Association for the Scientific Study of Consciousness)
  \item \years{2013}Dean's Fellowship (Columbia University)
  \item \years{2012}Postgraduate Research Scholarship (Victoria University of Wellington)
  \item School of Psychology Graduate Prize (Victoria University of Wellington)
  \item Victoria University Graduate Award (Victoria University of Wellington)
\end{itemize}

\section*{Publications \& Academic Contributions}
See \href{https://www.zotero.org/vuorre}{Zotero} or \href{https://scholar.google.com/citations?hl=en&user=I4DSy-8AAAAJ&view_op=list_works&sortby=pubdate}{Google Scholar} for the most up-to-date list of my publications.

\subsection*{Preprints}
\begin{itemize}
  \item Vuorre, M., Ballou, N., Hakman, T., Magnusson, K., \& Przybylski, A. K. (2023). Affective Uplift During Video Game Play: A Naturalistic Case Study. \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/z3ejx}
  \item Zloteanu, M., \& Vuorre, M. (2023). A Tutorial for Deception Detection Analysis or: How I Learned to Stop Aggregating Veracity Judgments and Embraced Bayesian Mixed Effects Models. \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/fdh5b}
  \item Vuorre, M., \& Przybylski, A. K. (2023). A multiverse analysis of the associations between internet use and well-being. \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/jp5nd}
  \item Johannes, N., Masur, P. K., Vuorre, M., \& Przybylski, A. K. (2021). How should we investigate variation in the relation between social media and well-being? \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/xahbg}
\end{itemize}

\subsection*{Journal articles}
\begin{itemize}
  \item \years{2024} Metcalfe, J., Xu, J., Vuorre, M., Siegler, R., Wiliam, D., \& Bjork, R. A. (2024). Learning from errors versus explicit instruction in preparation for a test that counts. \emph{British Journal of Educational Psychology}. \url{https://doi.org/10.1111/bjep.12651}
  \item \years{2023} Vuorre, M., \& Przybylski, A. K. (2023). Global Well-Being and Mental Health in the Internet Age. \emph{Clinical Psychological Science}. \url{https://doi.org/10.1177/21677026231207791}
  \item Miller, J., Mills, K. L., Vuorre, M., Orben, A., \& Przybylski, A. K. (2023). Impact of digital screen media activity on functional brain organization in late childhood: Evidence from the ABCD study. \emph{Cortex}. \url{https://doi.org/10.1016/j.cortex.2023.09.009}
  \item Vuorre, M., Magnusson, K., Johannes, N., Butlin, J., \& Przybylski, A. K. (2023). An intensive longitudinal dataset of in-game player behaviour and well-being in PowerWash Simulator. \emph{Scientific Data}. \url{https://doi.org/10.1038/s41597-023-02530-3}
  \item Vuorre, M., \& Przybylski, A. K. (2023). Estimating the association between Facebook adoption and well-being in 72 countries. \emph{Royal Society Open Science}. \url{https://doi.org/10.1098/rsos.221451}
  \item \years{2022} Syed Sheriff, R. J., Vuorre, M., Riga, E., Przybylski, A. K., Adams, H., Harmer, C. J., \& Geddes, J. R. (2022). A co-produced online cultural experience compared to a typical museum website for mental health in people aged 16–24: A proof-of-principle randomised controlled trial. \emph{Australian \& New Zealand Journal of Psychiatry}. \url{https://doi.org/10.1177/00048674221115648}
  \item Metcalfe, J., Vuorre, M., Towner, E., \& Eich, T. S. (2022). Curiosity: The effects of feedback and confidence on the desire to know. \emph{Journal of Experimental Psychology: General}. \url{https://doi.org/10.1037/xge0001284}
  \item Vuorre, M.\footnotemark[1], Johannes, N.\footnotemark[1], Magnusson, K., \& Przybylski, A. K.\footnotemark[1] (2022). Time spent playing video games is unlikely to impact well-being. \emph{Royal Society Open Science}. \url{https://doi.org/10.1098/rsos.220411}
  \item Johannes, N.\footnotemark[1], Vuorre, M.\footnotemark[1], Magnusson, K., \& Przybylski, A. K.\footnotemark[1] (2022). Time spent playing two online shooters has no measurable effect on aggressive affect. \emph{Collabra: Psychology}. \url{https://doi.org/10.1525/collabra.34606}
  \item Vuorre, M., Johannes, N., \& Przybylski, A. K. (2022). Three objections to a novel paradigm in social media effects research. \emph{PsyArXiv}. \url{https://doi.org/10.31234/osf.io/dpuya}
  \item \years{2021} Vuorre, M., Orben, A., \& Przybylski, A. K. (2021). There Is No Evidence That Associations Between Adolescents’ Digital Technology Engagement and Mental Health Problems Have Increased. \emph{Clinical Psychological Science}. \\ \url{https://doi.org/10.1177/2167702621994549}
  \item Vuorre, M., Zendle, D., Petrovskaya, E., Ballou, N., \& Przybylski, A. K. (2021). A Large-Scale Study of Changes to the Quantity, Quality, and Distribution of Video Game Play During a Global Health Pandemic. \emph{Technology, Mind, and Behavior}. \url{https://doi.org/10.1037/tmb0000048}
  \item Metcalfe, J., Kennedy-Pyers, T., \& Vuorre, M. (2021). Curiosity and the desire for agency: Wait, wait … don’t tell me! \emph{Cognitive Research: Principles and Implications}. \url{https://doi.org/10.1186/s41235-021-00330-0}
  \item Johannes, N.\footnotemark[1], Vuorre, M.\footnotemark[1], \& Przybylski, A. K.\footnotemark[1] (2021). Video game play is positively correlated with well-being. \emph{Royal Society Open Science}. \url{https://doi.org/10.1098/rsos.202049}
  \footnotetext[1]{Equal contribution.}
  \item Vuorre, M., \& Metcalfe, J. (2021). Measures of relative metacognitive accuracy are confounded with task performance in tasks that permit guessing. \emph{Metacognition and Learning.} \url{https://doi.org/10.1007/s11409-020-09257-1}

  \item \years{2020} Vuorre, M.\footnotemark[1], \& Crump, M. J. C.\footnotemark[1] (2020). Sharing and organizing research products as R packages. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-020-01436-x}
  \item \years{2019} Metcalfe, J., Brezler, J. C., McNamara, J., Maletta, G., \& Vuorre, M. (2019). Memory, stress, and the hippocampal hypothesis: Firefighters' recollections of the fireground. \emph{Hippocampus}. \url{https://doi.org/10.1002/hipo.23128}
  \item Bürkner, P.-C., \& Vuorre, M. (2019). Ordinal regression models in psychology: A tutorial. \emph{Advances in Methods and Practices in Psychological Science}. \url{https://doi.org/10.1177/2515245918823199}
  \item \years{2018} Bloom, P. A., Friedman, D., Xu, J., Vuorre, M., \& Metcalfe, J. (2018). Tip-of-the-tongue states predict enhanced feedback processing and subsequent memory. \emph{Consciousness and Cognition}. \url{https://doi.org/10.1016/j.concog.2018.05.010}
  \item Vuorre, M., \& Curley, J. P. (2018). Curating research assets: A tutorial on the Git version control system. \emph{Advances in Methods and Practices in Psychological Science}. \url{https://doi.org/10.1177/2515245918754826}
  \item Heino, M. T. J.\footnotemark[1], Vuorre, M.\footnotemark[1], \& Hankonen, N. (2018). Bayesian evaluation of behavior change interventions: A brief introduction and a practical example. \emph{Health Psychology and Behavioral Medicine: an Open Access Journal}. \url{https://doi.org/10.1080/21642850.2018.1428102}
  \item Chapman, S., Colvin, L. E., Vuorre, M., Cocchini, G., Metcalfe, J., Huey, E. D., \& Cosentino, S. (2018). Cross domain self-monitoring in anosognosia for memory loss in Alzheimer's disease. \emph{Cortex}. \url{https://doi.org/10.1016/j.cortex.2018.01.019}
  \item \years{2017} Vuorre, M. \& Bolger, N. (2017). Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-017-0980-9}
  \item Sidarus, N., Vuorre, M., \& Haggard, P. (2017). Integrating prospective and retrospective cues to the sense of agency: a multi-study investigation. \emph{Neuroscience of Consciousness}. \url{https://doi.org/10.1093/nc/nix012}
  \item Vuorre, M. \& Metcalfe, J. (2017). Voluntary action alters the perception of visual illusions. \emph{Attention, Perception, \& Psychophysics}. \url{https://doi.org/10.3758/s13414-017-1321-x}
  \item Vuorre, M. (2017). On time, causation, and the sense of agency. \emph{Journal of Consciousness Studies}. \url{http://www.ingentaconnect.com/contentone/imp/jcs/2017/00000024/F0020003/art00011}
  \item Sidarus, N., Vuorre, M., Metcalfe, J., \& Haggard, P. (2017). Investigating the prospective sense of agency: Effects of processing fluency, stimulus ambiguity, and response conflict. \emph{Frontiers in Psychology}. \url{https://doi.org/10.3389/fpsyg.2017.00545}
  \item Sidarus, N., Vuorre, M., \& Haggard, P. (2017). How action selection influences the sense of agency: An ERP study. \emph{NeuroImage}. \url{https://doi.org/10.1016/j.neuroimage.2017.02.015}
  \item \years{2016} Vuorre, M. \& Metcalfe, J. (2016). The relation between the sense of agency and the experience of flow. \emph{Consciousness and Cognition}. \url{https://doi.org/10.1016/j.concog.2016.06.001}
  \item \years{2013} Michael, R. B., Newman, E. J., Vuorre, M., Cumming, G., \& Garry, M. (2013). On the (non)persuasive power of a brain image. \emph{Psychonomic Bulletin \& Review}. \url{https://doi.org/10.3758/s13423-013-0391-6}
\end{itemize}

\subsection*{PhD thesis}
\begin{itemize}
  \item \years{2018} Vuorre, M. (2018). Using visual illusions to examine action-related perceptual changes. \url{https://academiccommons.columbia.edu/catalog/ac:73n5tb2rdf}
\end{itemize}

\subsection*{Scientific software}
\begin{itemize}
  \item \years{2017} Vuorre, M. (2017). bmlm: Bayesian Multilevel Mediation. R package version 1.3.4. \url{https://cran.r-project.org/package=bmlm}
\end{itemize}

\subsection*{Talks}
\begin{itemize}
  \item \years{2023} What can psychological science tell us about video games and their effects? \emph{\href{https://www.tilburguniversity.edu/campus/studium-generale/missing-link-impact-video-games}{Missing Link: How Video Games Impact Culture and Individuals}, Tilburg.}
  \item Intensive longitudinal dataset of video game play, well-being, and motivations: Case study of PowerWash Simulator. \emph{\href{https://www.psychologicalscience.org/conventions/icps-2023}{International Convention of Psychological Science}, Brussels.}
  \item Frontiers in Video Game Science. \emph{\href{https://www.psychologicalscience.org/conventions/icps-2023}{International Convention of Psychological Science}, Brussels.}
  \item \years{2022} Time spent playing video games is unlikely to impact well-being. \emph{International Communication Association meeting, Paris}.
  \item \years{2018} Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience. \emph{Columbia University}.
  \item \years{2017} A meta-analytic review of agency cues. \emph{European Society for Cognitive Psychology meeting, Potsdam, Germany}.
  \item \years{2016} The pragmatist's guide to studying free will. \emph{Science of Consciousness meeting, Tucson, Arizona}.
  \item Voluntary actions cause a temporal rate-shift in visual awareness: Evidence from visual illusions. \emph{Science of Consciousness meeting, Tucson, Arizona}.
  \item \years{2015} Voluntary action and time perception. \emph{Toward a Science of Consciousness meeting, Helsinki, Finland}.
\end{itemize}

\subsection*{Other articles}
\begin{itemize}
  \item \years{2016} Vuorre, M. (December 5, 2016). Introduction to data analysis using R. \emph{JEPS Bulletin}. \url{http://blog.efpsa.org/2016/12/05/introduction-to-data-analysis-using-r/}
  \item \years{2014} Vuorre, M. (April 29, 2014). What your name says about how believable you are. \emph{Scientific American}. \url{https://www.scientificamerican.com/article/what-your-name-says-about-how-believable-you-are/}
\end{itemize}

\section*{Public Engagement \& Media}

\begin{itemize}
  \item \years{2023} Teknologia ei tuhonnut kansan psyykettä (December 25, 2023). Interview at \emph{\href{https://www.hs.fi/visio/art-2000010069351.html}{Helsingin Sanomat}} (Finland)
  \item Ny studie: Inga bevis för att internet skadar vårt välmående (December 17, 2023). Interview at \emph{\href{https://www.svt.se/nyheter/inrikes/ny-studie-inga-bevis-for-att-internet-skadar-vart-valmaende--x52qwt}{SVT}} (Sweden)
  \item \years{2021} 6 Minute English: Is technology harmful to youngsters? (September 6, 2021). Interview at \emph{\href{https://www.bbc.co.uk/learningenglish/english/features/6-minute-english/ep-210906}{BBC Learning English}} (UK)
  \item Tech does not impact teenage mental health (May 4, 2021). Interview at \emph{\href{https://www.bbc.co.uk/programmes/w3ct1lry}{BBC Digital Planet}} (UK)
\end{itemize}

\section*{Teaching}

\subsection*{Courses}
\begin{itemize}
  \item \years{2024-} Experimental research (Tilburg University)
  \item \years{2023-} Consumer Analytics using Big Data (Tilburg University)
  \item \years{2021-2022} Experiments for Social Data Science (University of Oxford)
\end{itemize}

\subsection*{Teaching Assistantships}
\begin{itemize}
  \item \years{2018} Statistics for Behavioral Scientists (Columbia University)
  \item \years{2017} Introduction to Statistical Modeling in Psychology (Columbia University)
  \item \years{2016} Analysis of Change (Columbia University)
  \item \years{2015} Experimental Psychology: Human Behavior (Columbia University)
  \item \years{2014 \& 2016} The Science of Psychology (Columbia University)
  \item \years{2013} Visual Perception (Victoria University of Wellington)
  \item \years{2011 \& 2013} Introduction to Psychology (Victoria University of Wellington)
\end{itemize}

\subsection*{Workshops}
\begin{itemize}
  \item \years{2023} Data visualization workshop (Tilburg University; Tilburg PhD Platform)
  \item \years{2020} Bayesian regression modelling with brms (University of Zürich; \url{https://mvuorre.github.io/brms-workshop/})
  \item \years{2019} Bayesian modelling with the Stan probabilistic programming language (Columbia University; \url{https://github.com/mvuorre/ulam})
  \item \years{2018} Hierarchical modelling of change over time (University of Aberdeen)
  \item \years{2017} Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience (Rutgers University; \url{https://github.com/mvuorre/2017-rutgers-mediation})
\end{itemize}

\section*{Service to the profession}

\begin{itemize}
  \item Member of \href{https://www.tilburguniversity.edu/research/tilburg-young-academy/members}{Tilburg Young Academy}
  \item Recommender at \href{https://rr.peercommunityin.org/public/user_public_page?userId=1570}{Peer Community In Registered Reports}
\end{itemize}

I have acted as a peer reviewer for Advances in Methods and Practices in Psychological Science; Acta Psychologica; Attention, Perception, \& Psychophysics; British Journal of Mathematical and Statistical Psychology; International Journal of Psychology; Journal of Adolescence; Journal of Consciousness Studies; Journal of the Experimental Analysis of Behavior; Journal of Experimental Psychology: General; Nature Human Behaviour; Peer Community In Registered Reports; Psychology of Consciousness; and Royal Society Open Science. I always sign my reviews.

\vfill{}

\end{document}
