%!TEX program = xelatex
%!TeX TS-program = XeLaTeX
%!TEX encoding = UTF-8 Unicode
% \documentclass[12pt, letterpaper]{article} % Switch between letter and a4
\documentclass[12pt, a4paper]{article}

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{textwidth=5.5in, textheight=9.5in, marginparsep=12pt, marginparwidth=.6in}
\parindent 2.5cm
\parskip 0cm
\linespread{1.1}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Scale = 1.0, Ligatures={Common}, BoldFont={Libertinus Serif Bold}, ItalicFont={Libertinus Serif Italic}]{Libertinus Serif}
% Year as margin note on left
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\reversemarginpar
% Footnotes as symbols
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\upshape\Large}
\subsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\subsubsectionfont{\rmfamily\mdseries\upshape\normalsize} 

% List format
\usepackage{fontspec} 
\usepackage{enumitem}
\setlist[itemize]{label={},itemindent=-1em,leftmargin=1em,itemsep=0em}

% PDF SETUP
\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={Matti Vuorre - vita},pdfauthor={Matti Vuorre}]{hyperref} 
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 
\urlstyle{same}

% Content
\begin{document}
\noindent
{\LARGE Matti Vuorre}\\[.25cm]
Columbia University\\
406 Schermerhorn Hall\\
1190 Amsterdam Avenue\\
New York, NY 10027, U.S.A.\\
\textsc{email}: \href{mailto:mv2521@columbia.edu}{mv2521@columbia.edu}\\
\textsc{website}: \href{https://vuorre.netlify.com}{https://vuorre.netlify.com}\\
\textsc{cv updated}: \today

\section*{Current Position}
\emph{Postdoctoral Research Scientist}, Columbia University, New York (May 2018 -)

\section*{Areas of Specialization}
cognitive psychology \ • \ metacognition \ • \ applied statistics

\section*{Education}
\years{2018}\textsc{PhD}, Columbia University, USA\\
\years{2017}\textsc{MPhil}, Columbia University, USA\\
\years{2015}\textsc{M.A}, Columbia University, USA\\
\years{2013}\textsc{BSc (Hons)} in Psychology, Victoria University of Wellington, New Zealand\\
\years{2012}\textsc{BSc} in Psychology and Philosophy, Victoria University of Wellington, New Zealand

\section*{Grants, Honors \& Awards}
\years{2016}Leo Rubinstein Endowed Fellowship (Columbia University)\\
Graduate Student Travel Award (Psychonomic Society)\\
\years{2015}Leo Rubinstein Endowed Fellowship (Columbia University)\\
Edward E. Smith Memorial Award in Cognitive Neuroscience (Columbia University)\\
Best Student Poster Award (Association for the Scientific Study of Consciousness)\\
\years{2013}Dean's Fellowship (Columbia University)\\
\years{2012}Postgraduate Research Scholarship (Victoria University of Wellington)\\
School of Psychology Graduate Prize (Victoria University of Wellington)\\
Victoria University Graduate Award (Victoria University of Wellington)

\section*{Publications \& Academic Contributions}

\subsection*{Works in progress}
\begin{itemize}
\item Vuorre, M., \& Metcalfe, J. (ms in prep). Unskilled but not so unaware.
\item Towner, E.\footnotemark[1], Vuorre, M.\footnotemark[1], \& Metcalfe, J.\footnotemark[1] (ms in prep). Confidence in errors is associated with increased curiosity.
\end{itemize}

\footnotetext[1]{Equal contribution.}

\subsection*{Journal articles}
\begin{itemize}[label={},itemindent=-1em,leftmargin=1em,itemsep=0em]
\item \years{2019} Metcalfe, J., Brezler, J. C., McNamara, J., Maletta, G., \& Vuorre, M. (2019). Memory, stress, and the hippocampal hypothesis: Firefighters' recollections of the fireground. \emph{Hippocampus}. \url{https://doi.org/10.1002/hipo.23128}
\item Bürkner, P.-C., \& Vuorre, M. (2019). Ordinal Regression Models in Psychology: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}. \url{https://doi.org/10.1177/2515245918823199}
\item \years{2018} Bloom, P. A., Friedman, D., Xu, J., Vuorre, M., \& Metcalfe, J. (2018). Tip-of-the-tongue states predict enhanced feedback processing and subsequent memory. \emph{Consciousness and Cognition}. \url{https://doi.org/10.1016/j.concog.2018.05.010}
\item Vuorre, M., \& Curley, J. P. (2018). Curating Research Assets: A Tutorial on the Git Version Control System. \emph{Advances in Methods and Practices in Psychological Science}. \url{https://doi.org/10.1177/2515245918754826}
\item Heino, M. T. J.\footnotemark[1], Vuorre, M.\footnotemark[1], \& Hankonen, N. (2018). Bayesian evaluation of behavior change interventions: A brief introduction and a practical example. \emph{Health Psychology and Behavioral Medicine: an Open Access Journal}. \url{https://doi.org/10.1080/21642850.2018.1428102}
\item Chapman, S., Colvin, L. E., Vuorre, M., Cocchini, G., Metcalfe, J., Huey, E. D., \& Cosentino, S. (2018). Cross domain self-monitoring in anosognosia for memory loss in Alzheimer's disease. \emph{Cortex}. \url{https://doi.org/10.1016/j.cortex.2018.01.019}
\item \years{2017} Vuorre, M. \& Bolger, N. (2017). Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-017-0980-9}
\item Sidarus, N., Vuorre, M., \& Haggard, P. (2017). Integrating prospective and retrospective cues to the sense of agency: a multi-study investigation. \emph{Neuroscience of Consciousness}, 3(1). \url{https://doi.org/10.1093/nc/nix012}
\item Vuorre, M. \& Metcalfe, J. (2017). Voluntary action alters the perception of visual illusions. \emph{Attention, Perception, \& Psychophysics}. \url{https://doi.org/10.3758/s13414-017-1321-x}
\item Vuorre, M. (2017). On Time, Causation, and the Sense of Agency. \emph{Journal of Consciousness Studies}, 24(3–4), 203–215. \url{http://www.ingentaconnect.com/contentone/imp/jcs/2017/00000024/F0020003/art00011}
\item Sidarus, N., Vuorre, M., Metcalfe, J., \& Haggard, P. (2017). Investigating the prospective sense of agency: Effects of processing fluency, stimulus ambiguity, and response conflict. \emph{Frontiers in Psychology}, 8, 545. \url{https://doi.org/10.3389/fpsyg.2017.00545}
\item Sidarus, N., Vuorre, M., \& Haggard, P. (2017). How action selection influences the sense of agency: An ERP study. \emph{NeuroImage}, 150, 1–13. \url{https://doi.org/10.1016/j.neuroimage.2017.02.015}
\item \years{2016} Vuorre, M. \& Metcalfe, J. (2016). The relation between the sense of agency and the experience of flow. \emph{Consciousness and Cognition}, 43. \url{https://doi.org/10.1016/j.concog.2016.06.001}
\item \years{2013} Michael, R. B., Newman, E. J., Vuorre, M., Cumming, G., \& Garry, M. (2013). On the (non)persuasive power of a brain image. \emph{Psychonomic Bulletin \& Review}, 20(4), 720–725. \url{https://doi.org/10.3758/s13423-013-0391-6}
\end{itemize}

\subsection*{Scientific software}
\begin{itemize}
\item \years{2017} Vuorre M. (2017). bmlm: Bayesian Multilevel Mediation. \\ \url{https://cran.r-project.org/package=bmlm}
\end{itemize}

\subsection*{Talks}
\begin{itemize}
\item \years{2018} Vuorre, M. (2018, February). Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience. Talk presented at Columbia University.
\item \years{2017} Vuorre, M., Sidarus, N., \& Metcalfe, J. (2017, September). A Meta-Analytic Review of Agency Cues. Talk presented at the \emph{European Society for Cognitive Psychology} meeting, Potsdam, Germany.
\item \years{2016} Vuorre, M. (2016, April). The Pragmatist's Guide to Studying Free Will. Talk presented at the \emph{Science of Consciousness} meeting, Tucson, Arizona.
\item \years{2016} Vuorre, M. (2016, April). Voluntary Actions Cause a Temporal Rate-Shift in Visual Awareness: Evidence from visual illusions. Talk presented at the \emph{Science of Consciousness} meeting, Tucson, Arizona.
\item \years{2015} Vuorre, M. \& Metcalfe, J. (2015, June). Voluntary Action and Time Perception. Talk presented at the \emph{Toward a Science of Consciousness} meeting, Helsinki, Finland.
\end{itemize}

\subsection*{Conference posters}
\begin{itemize}
\item \years{2019} Vuorre, M. \& Metcalfe, J. (2019, March). Confidence-Accuracy Relationship in Mathematics. Poster presented (by JM) at the International Convention of Psychological Science, Paris, France.
\item Vuorre, M., Xu, J., \& Metcalfe, J. (2019, January). Learning from Errors. Poster presented at the IES Annual Principal Investigators Meeting, Washington DC, USA.
\item \years{2018} Vuorre, M. \& Metcalfe, J. (2018, November). Learning from Errors: Students' Confidence and Instructional Choices. Poster presented at the Psychonomic Society annual meeting, New Orleans, USA.
\item \years{2017} Vuorre, M. \& Bolger, N. (2017, November). Within-Subject Mediation Analysis for Experimental Data in Cognitive Psychology and Neuroscience. Poster presented at the Psychonomic Society annual meeting, Vancouver, Canada.
\item Vuorre, M., Metcalfe, J., Friedman, D., Bloom, P., Xu, J., \& Bolger, N. (2017, September). Within-Subject Mediation Analysis for Experimental Data in Cognitive Psychology and Neuroscience. Poster presented at the European Society for Cognitive Psychology, Potsdam, Germany.
\item Metcalfe, J., Bloom, P. A., Xu, J., Vuorre, M., \& Friedman, D. (2017, March). Tip-of-the-Tongue States Enhance Processing to Feedback. Poster presented at the Cognitive Neuroscience Society annual meeting, San Fransisco, USA.
\item \years{2016} Vuorre, M., Metcalfe, J. (2016, November). The relation between the sense of agency and the experience of flow. Poster presented at the Psychonomic Society annual meeting, Boston, USA.
\item Sidarus, N., Vuorre, M., Haggard, P. (2016, September). Integrating Prospective and Retrospective Cues to the Sense of Agency: A Multi-Study Investigation. Poster presented at the British Association for Cognitive Neuroscience annual meeting, Budapest, Hungary.
\item \years{2015} Vuorre, M., Metcalfe, J. (2015, July). Voluntary Actions Compress the Experience of Time. Poster presented at the Association for the Scientific Study of Consciousness annual meeting, Paris, France.
\item Vuorre, M., Metcalfe, J. (2015, May). Voluntary Actions Compress the Experience of Time. Poster presented at the Association for Psychological Science annual meeting, New York, USA.
\item \years{2014} Vuorre, M., Metcalfe, J. (2014, November). Voluntary Action and Time Perception. Poster presented at the Psychonomic Society annual meeting, Long Beach, USA.
\item Vuorre, M., Metcalfe, J. (2014, November). Voluntary Action and Time Perception. Poster presented at the Association for the Scientific Study of Consciousness annual meeting, Brisbane, Australia.
\item \years{2012} Vuorre, M. (2012, April). How shifts in tense in memory narratives affect people. Conference presentation at KiwiCAM, Wellington, New Zealand.
\end{itemize}

\subsection*{Other articles}
\begin{itemize}
\item \years{2016} Vuorre, M. (2016, December 5). Introduction to Data Analysis using R. \emph{JEPS Bulletin}. \url{http://blog.efpsa.org/2016/12/05/introduction-to-data-analysis-using-r/}
\item \years{2014} Vuorre, M. (April 29, 2014), What Your Name Says About How Believable You Are, \emph{Scientific American}. \url{https://www.scientificamerican.com/article/what-your-name-says-about-how-believable-you-are/}
\end{itemize}

\section*{Teaching}

\subsection*{Workshops taught}
\begin{itemize}
\item \years{2019} Bayesian modelling with the Stan probabilistic programming language (Columbia University; \url{https://github.com/mvuorre/ulam})
\item \years{2018} Hierarchical modelling of change over time (University of Aberdeen)
\item \years{2017} Within-subject mediation analysis for experimental data in cognitive psychology and neuroscience (Rutgers University; \url{https://github.com/mvuorre/2017-rutgers-mediation})
\end{itemize}

\subsection*{Teaching Assistantships}
\years{2018}
Statistics for Behavioral Scientists (Columbia University)\\
\years{2017}
Introduction to Statistical Modeling in Psychology (Columbia University)\\
\years{2016}
Analysis of Change (Columbia University)\\
The Science of Psychology (Columbia University)\\
\years{2015}
Experimental Psychology: Human Behavior (Columbia University)\\
\years{2014}
The Science of Psychology (Columbia University)\\
\years{2013}
Visual Perception (Victoria University of Wellington)\\
Introduction to Psychology (Victoria University of Wellington)\\
\years{2011}
Introduction to Psychology (Victoria University of Wellington)


\section*{Service to the profession}

\subsection*{Panels organized}
Metacognition of Agency workshop (2015, May), Co-organizer and co-chair.

\subsection*{Peer review service}
Acta Psychologica \\
Attention, Perception, \& Psychophysics \\
Journal of Consciousness Studies \\
Journal of the Experimental Analysis of Behavior \\
Psychology of Consciousness

\vfill{}

\end{document}